PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2021-11-29 main.tex
More content

% Mention Rayleigh distribution
In the `nominal' case, we give the bodies a bulk density of 3 g cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, where $e_{h} = e a/r_{h}$ (define this in the previous section instead) which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$. These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by a factor of $\sim$ 7100, which produces $\alpha = 1$. To vary $\beta$, the eccentricity dispersion is increased. For the high-$\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.
% Important note: need to use f=6 for the low alpha case, otherwise the simulation takes forever. Do these alpha values reflect the artifically enhanced collision cross section im using?
% Should I choose beta = 1 instead? I did beta >> 1 to see if inelastic mergers will cool things off. Havent decided if that's important here
% Another concern: using too large of a beta makes the apo-peri distances larger than the width of the annulus

@@

%If we run a cooler version of the high-beta simulations (so that the masses can evolve further), does the high alpha case end up cooler? If so, that would be a second indication that 'collisions are driving the dynamics at high alpha'.

@@

@@

@@

\begin{figure}
\begin{center}
    \includegraphics[width=0.5\textwidth]{figures/alpha_pl_frac.png}
    \caption{Caption goes here.\label{fig:alpha_pl_frac}}
\end{center}
\end{figure}

@@

% is there a clever, succinct way to show the evolution of sigma/Sigma in each period bin? to demonstrate that the accretion boundary is static

>>>>

% Mention Rayleigh distribution
In the `nominal' case, we give the bodies a bulk density of 3 g cm$^{-3}$, and $\left< e^{2} \right>^{1/2} = 4 e_{h}$, where $e_{h} = e a/r_{h}$ (define this in the previous section instead) which corresponds to $\alpha = 3.6 \times 10^{-2}$ and $\beta = 3.4 \times 10^{-3}$. These parameters are chosen to match the initial conditions of \citet{kokubo98}, which gave rise to oligarchic growth. To vary the value of $\alpha$, we alter the bulk density of the particles. In the high-$\alpha$ case, the bulk density is reduced by a factor of $\sim$ 7100, which produces $\alpha = 1$. To vary $\beta$, the eccentricity dispersion is increased. For the high-$\beta$ case, $\left< e^{2} \right>^{1/2}$ is increased to $1500 e_{h}$, which corresponds to $\beta = 15,000$.

@@

@@

% Additional idea: run a simulation with an oligarch embedded in a disk of planetesimals for large and small alpha. Allow oligarch and planetesimals to collide. What does the eccentricity evolution of the oligarch look like in each case?
% See equation 32 from goldreich 2004: b_scat ~ sqrt(u/vh) R_H
% How does b_scat compare to particle size here?

% One thing im still not clear on: In dispersion dominated regime, distant encounters are what drive VS + DF. These encounters happen well outside of the Hill sphere. Why does it appear to matter if the geometric cross section fills a significant chunk of the hill sphere? And why doesn't the velocity dispersion (beta large or small) appear to matter?

@@

To ensure that the boundary seen near 60 days in orbital period is not simply a transient product of the inside out growth throughout the disk, we examine the time evolution of $\sigma/\Sigma$ at multiple locations. In figure \ref{fig:pl_frac_time}, the value of $\sigma/\Sigma$ is plotted as a function of time in 10 orbital period bins. Bins interior to 60 days are indicated with a dashed line, while those exterior are indicated with a solid line. The planetesimal surface density fraction has decelerated and is approaching an asymptotic value in all cases. In the inner disk, this is driven by the near-total depletion of the planetesimal reservoir. In the outer disk, dynamical friction between the embryos and planetesimals throttles subsequent accretion.

% Since we are using f=6, do we want to stick to plotting things in terms of timestep number, and then provide rescaled time estimates at the end?

@@

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/alpha_pl_frac.png}
    \caption{Caption goes here.\label{fig:alpha_pl_frac}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/pl_frac_time.png}
    \caption{Caption goes here.\label{fig:pl_frac_time}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/surfden_profiles.png}
    \caption{Caption goes here.\label{fig:surfden_profiles}}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{figures/surfden_iso.png}
    \caption{Caption goes here.\label{fig:surfden_iso}}
\end{center}
\end{figure*}

@@
